#This code can be used to apply rake weights iteratively to a data set containing multiple groups (i.e. 4 table cats in AS & HS).
#Weights will be applied to each data subset independently. This can be done using unique weighting targets for each segment (demonstrated here), or identical weighting targets (not demonstrated). 

#For simplified rake weighting procedures, see Dan's git 'rakewt-ashs/weight-example.R'


##Load packages and data
```{r}
library(anesrake)
library(weights)
library(haven)
library(gtools)

data <- read.csv("C:/Users/Patrick/Southwick Associates/ASA - ASA-19-01 Developing Angler Personas/Work files/Data & Syntax/binary_data_final.csv")
```

##If variables are not factors, ensure that they're converted into factors. 
###The following macro will accomplish this for the 4 dimensions on which we'll rake weight. 
```{r}
fac_mac <- defmacro(var, expr={
  data$var <- as.factor(data$var)
  }
)

fac_mac (Region)
fac_mac (female)
fac_mac (AgeCat)
fac_mac (avidity)
```


##For weighting schemes that use varied targets (this project weights each segment w/i ASA-19-01 individually):
###read in a csv with the distribution for each segment. 
###Create lists containing the weighting targets. Each segment (of 7 total) will have a list which will be used for weighting. 
```{r}
raw_dist <- read.csv("C:/Users/Patrick/Southwick Associates/ASA - ASA-19-01 Developing Angler Personas/Work files/Data & Syntax/Final Data Sets/Dist_for_Wts.csv", row.names=1)
Dist_for_Wts <- (raw_dist/100)

pop_mac <- defmacro(seg, new_list, expr={
  new_list <- list(
      female = c("0" = Dist_for_Wts[1, seg], "1" = Dist_for_Wts[2, seg]), 
      AgeCat = c("0" = Dist_for_Wts[3, seg], "1" = Dist_for_Wts[4, seg], "2" = Dist_for_Wts[5, seg]), 
      avidity = c("0" = Dist_for_Wts[6, seg], "1" = Dist_for_Wts[7, seg], "2" = Dist_for_Wts[8, seg], 
                  "3" = Dist_for_Wts[9, seg], "4" = Dist_for_Wts[10, seg], "5" = Dist_for_Wts[11, seg]),
      Region = c("1" = Dist_for_Wts[12, seg], "2" = Dist_for_Wts[13, seg], "3" = Dist_for_Wts[14, seg], 
                 "4" = Dist_for_Wts[15, seg]))

      new_list$female <- new_list$female/sum(new_list$female)
      new_list$AgeCat <- new_list$AgeCat/sum(new_list$AgeCat)
      new_list$avidity <- new_list$avidity/sum(new_list$avidity)
      new_list$Region <- new_list$Region/sum(new_list$Region)

})

pop_mac (1, seg1)
pop_mac (2, seg2)
pop_mac (3, seg3)
pop_mac (4, seg4)
pop_mac (5, seg5)
pop_mac (6, seg6)
pop_mac (7, seg7)
```

##The following function will subset the data into segments and apply rake weights to each segment. 
##This will result in 7 different data sets, which are summarized and bound back together with rbind on the last line. 
```{r}
seg_est_wts <- function(seg, pop, print_name = "", idvar = "Unique", cap = 100){
    data <- subset(data, data$cluster==seg)
    wts <- anesrake(pop, data, caseid = data[[idvar]], force1 = TRUE, cap = cap)
    data$rake_wt <- wts$weightvec
    data
}
seg1_wtd <- seg_est_wts(1, seg1)
seg2_wtd <- seg_est_wts(2, seg2)
seg3_wtd <- seg_est_wts(3, seg3)
seg4_wtd <- seg_est_wts(4, seg4)
seg5_wtd <- seg_est_wts(5, seg5)
seg6_wtd <- seg_est_wts(6, seg6)
seg7_wtd <- seg_est_wts(7, seg7)

print(summary(seg1_wtd$rake_wt))
print(summary(seg2_wtd$rake_wt))
print(summary(seg3_wtd$rake_wt))
print(summary(seg4_wtd$rake_wt))
print(summary(seg5_wtd$rake_wt))
print(summary(seg6_wtd$rake_wt))
print(summary(seg7_wtd$rake_wt))

data_wtd <- rbind(seg1_wtd, seg2_wtd, seg3_wtd, seg4_wtd, seg5_wtd, seg6_wtd, seg7_wtd)
```
